Displacement field paper

### 2016-09-12 ms_disp1/ms_disp1.tex
displacement field Wiener filters

\begin{abstract}
Abstract goes here.
\end{abstract}

@@

\section{Introduction}\label{sec.intro}
Introduction goes here. Citation \cite{2000ApJ...534L..19P}. Bold type use $\bs{v}=\vec{v}$.

\section{Method}\label{sec.method}
Method goes here.

\begin{figure} \centering
  \includegraphics[width=1.0\linewidth]{fig1.pdf}
  \caption{Caption goes here.}
  \label{fig.1}
\end{figure}

>>>>

\begin{abstract}
In this paper, we discover the ability of using displacement field to reconstruct initial linear perturbations in the early universe.
\end{abstract}

@@

\section{Introduction}\label{sec.intro}
Introduction goes here. Citation example \cite{2013MNRAS.436..540H}.
Cite Hong-Ming's 1D paper.

The rest of this paper is structured as follows. In section \ref{sec.method} we describe the simulation and reconstruction algorithm. In section \ref{sec.results} we show the results of the reconstruction. Discussion and conclusion are in \ref{sec.discussion}.

\section{Method}\label{sec.method}
Method goes there.

\subsection{Simulation}
Cosmological parameters, simulation parameters.

Initial conditions, get linear density field $\delta_L$. Run simulation by code {\tt CUBE} and get the nonlinear density field $\delta$ at $z=0$. {\tt CUBE} uses particle-ID (PID) to record the initial location of particles, and the information is tracked until the $z=0$ and we can get the displacement vector ${\bs s}\equiv{\bs x}-{\bs q}$ for every particle. Then these vectors are interpolated onto the initial Lagrangian coordinates ${\bs q}$ of particles and we get the displacement field ${\bs s}({\bs q})$.

\subsection{Reconstruction}
Get the raw reconstructed density field $\delta_R=-\nabla\cdot{\bs s}({\bs q})$.

%\begin{figure}[t] \centering
%  \includegraphics[width=1.0\linewidth]{fig1.pdf}
%  \caption{Caption goes here.}
%  \label{fig.1}
%\end{figure}

\section{Results}\label{sec.results}

Wiener filter.

We try to decompose $\delta_L$ into two components,
\begin{equation}\label{eq.decompose}
    \delta_L=r\delta_R+\delta_N,
\end{equation}
where $r\delta_R$ is completely correlated with $\delta_L$, and the uncorrelated part $\delta_N$ is generated by the nonlinear evolution. To do this, we first correlate equation (\ref{eq.decompose}) with $\delta_R$,
\begin{equation}\label{eq.correlate}
    \left\langle\delta_L\delta_R\right\rangle
    =r\left\langle\delta_R\delta_R\right\rangle
    +\left\langle\delta_N\delta_R\right\rangle,
\end{equation}
and vanish the second term in the right-hand-side. Then the $r$ is given by $\left\langle\delta_L\delta_R\right\rangle / \left\langle\delta_R\delta_R\right\rangle$ and mode-coupling term $\delta_N=\delta_L-r\delta_R$. We next square equation (\ref{eq.decompose}) and gives
\begin{equation}\label{eq.square}
    \left\langle\delta_L\delta_L\right\rangle
    =r^2\left\langle\delta_R\delta_R\right\rangle
    +\left\langle\delta_N\delta_N\right\rangle
    +2r\left\langle\delta_R\delta_N\right\rangle,
\end{equation}
and the third term of right-hand-side also vanishes. By defining
\begin{equation}
    \left\langle\delta_L\delta_L\right\rangle
    =b^2\left\langle\delta_R\delta_R\right\rangle,
\end{equation}
we write
\begin{equation}
    \left\langle\delta_N\delta_N\right\rangle=(b^2-r^2)\left\langle\delta_R\delta_R\right\rangle
\end{equation}
and a Wiener filter can be constructed as
\begin{equation}
    W=\frac{r^2\left\langle\delta_R\delta_R\right\rangle}
    {r^2\left\langle\delta_R\delta_R\right\rangle+\left\langle\delta_N\delta_N\right\rangle}
    =\frac{r^2}{b^2}.
\end{equation}

From equation (\ref{eq.decompose}), multiplying $W$, we obtain the optimal reconstructed linear density field by
\begin{equation}
    \tilde\delta_L=rW\delta_R=\frac{r^3}{b^2}\delta_R.
\end{equation}
From equation (\ref{eq.square}), multiplying $W^2$, the reconstructed linear power spectrum is giving by
\begin{equation}
\begin{aligned}
    \tilde{P}&=W^2\left\langle\delta_L\delta_L\right\rangle  \\
    &=r^2W^2\left\langle\delta_R\delta_R\right\rangle +W^2\left\langle\delta_N\delta_N\right\rangle  \\
    &=b^2W^2\left\langle\delta_R\delta_R\right\rangle  \\
    &=r^4b^{-2}\left\langle\delta_R\delta_R\right\rangle.
\end{aligned}
\end{equation}
